Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-04 paper.tex
chore: rewrite GNN section and add a problem definition (probably to general, we need to think about it)

\section{Background and Motivation}
Field-based RL draws upon research areas that were not previously considered in traditional RL. 
%
This section provides an overview of three key concepts that underpin this approach, 
 namely 
 field-based coordination --i.e., coordinating multi-agent systems through computational fields--, 
 \ac{GNN} --i.e., a novel type of neural network architecture designed to process graph-structured data--, 
 and \ac{MAARL} ---i.e., a large number of agents learning a collective policy to achieve a global goal.
\label{sec:background}
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks}
Over the years, several different neural networks have been proposed to solve specific tasks, ranging from 
  simple \ac{MLP} to \ac{CNN}~\cite{oshea2015introduction}.
%
Whereas \ac{CNN} is designed to be used with image and spatial-like data (e.g., audio),
 \ac{GNN} is a novel model used to process graph-structured data. 
%
Let $ G = (V, E) $ be a graph, where $ V $ is the set of nodes and $ E $ is the set of edges. 
%
Given $X_v$ a feature vector associated to each node $v \in V$, 
 the goal of a GNN is to learn the node embedding $X'_v$ for each node $v \in V$.
 In modern GNNs, the node embedding $X'_v$ is computed by aggregating information from the node's neighbours $N(v)$,
  and then combining it with the node's current embedding $X_v$.
% 
Formally, a GNN can be defined by two phases:
\begin{equation}
a_{v}^{(k)}=\operatorname{AGGREGATE}^{(k)}\left(\left\{h_{u}^{(k-1)}: u \in \mathcal{N}(v)\right\}\right)   
\end{equation}
\begin{equation}
h_{v}^{(k)}=\operatorname{COMBINE}^{(k)}\left(h_{v}^{(k-1)}, a_{v}^{(k)}\right)
\end{equation}
where $h_{v}^{k}$ is the embedding of node $v$ at the $k$-th layer, 
 $\mathcal{N}(v)$ is the set of neighbors of node $v$ computed from $E$.
%
The differential part come into play in the $\operatorname{COMBINE}$ function, 
 which is usually a differentiable function such as a neural network layer.
%
$\operatorname{AGGREGATE} $ instead is a function that aggregates the information from the neighbours of a node $v$
  and it could be a simple sum or a more complex function such as a neural network layer.
%
This formulation allows GNNs to effectively process and extract features from graph-structured data by iteratively aggregating and transforming information from the node's neighbours.

>>>>

\section{Background and Motivation}
\label{sec:background}
In this section, we aim to provide a concise overview of the system we intend to address, 
 starting with a system definition. 
%
We then proceed to discuss relevant research areas that inform our approach. 
%
Finally, we present a formalization of the problem and a discussion of the motivations behind our proposed work.
%Field-based RL draws upon research areas that were not previously considered in traditional RL. 
%
%This section provides an overview of three key concepts that underpin this approach, 
% namely 
% field-based coordination --i.e., coordinating multi-agent systems through computational fields--, 
% \ac{GNN} --i.e., a novel type of neural network architecture designed to process graph-structured data--, 
% and \ac{MAARL} ---i.e., a large number of agents learning a collective policy to achieve a global goal.

\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Problem definition}
This article focuses on the definition of decentralized collective intelligence within the context of large-scale distributed systems. 
%
Specifically, we consider the case where agents can interact through 1-hop neighbourhood connections and have a local perception of the environment, 
 which is typical in systems such as swarm robotics or large-scale IoT.

We model the system at a given time instance as a graph, $G = (V, E)$, 
 where $E$ defines the neighbourhood relations for each participating node, 
 and $V$ identifies the nodes present in the graph at that time. 
% 
Each node $v$ is associated with an observation (or feature set), $o_v$, 
 which can come from sensors installed on it and messages received from the neighbourhood in the previous step.

Our goal is to find a homogeneously distributed controller $\pi$ that, 
 starting from only local configurations, leads 
 the system to achieve a graph $G_T$ that satisfies certain collective requirements through cooperation, such as spatial area coverage, phenomena tracking, and robot aggregation.
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks}
Over the years, several different neural networks have been proposed to solve specific tasks, ranging from 
  simple \ac{MLP} to \ac{CNN}~\cite{oshea2015introduction}.
%
Whereas \ac{CNN} is designed to be used with image and spatial-like data (e.g., audio),
 \ac{GNN} is a novel model used to process graph-structured data. 
%
Let $ G $ be the above-defined graph.
%
Given $o_v$ a feature vector associated with each node $v \in V$, 
 the goal of a GNN is to learn the node embedding $h_v$ for each node $v \in V$.
 In modern GNNs, the node embedding $h_v$ is computed by aggregating information from the node's neighbours $N(v)$,
  and then combining it with the node's current embedding $h_v$.
% 
Formally, a GNN can be defined by two phases:
\begin{equation}
a_{v}^{(k)}=\operatorname{AGGREGATE}^{(k)}\left(\left\{h_{u}^{(k-1)}: u \in \mathcal{N}(v)\right\}\right)   
\end{equation}
\begin{equation}
h_{v}^{(k)}=\operatorname{COMBINE}^{(k)}\left(h_{v}^{(k-1)}, a_{v}^{(k)}\right)
\end{equation}
where $h_{v}^{k}$ is the embedding of node $v$ at the $k$-th layer ($h_v^0 = o_v$), 
 $\mathcal{N}(v)$ is the set of neighbors of node $v$ computed from $E$.
%
The differential part come into play in the $\operatorname{COMBINE}$ function, 
 which is usually a differentiable function such as a neural network layer.
%
$\operatorname{AGGREGATE} $ instead is a function that aggregates the information from the neighbours of a node $v$
  and it could be a simple sum or a more complex function such as a neural network layer.
%
This formulation allows GNNs to effectively process and extract features from graph-structured data by iteratively aggregating and transforming information from the node's neighbours.
